---
title: "Create Test and Train"
author: "Rachel Jordan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data

```{r}
#load tidyverse
require(tidyverse)

#load data set
modeling_data_raw <- read.csv("All Data for Modeling.csv",header=T)
modeling_data <- modeling_data_raw

#drop property ID, parcel ID, lastsaledate
modeling_data <- modeling_data %>% 
  select(-c(PropertyID,ParcelID,LastSaleDate))

#relevel factors
modeling_data$PhysicalCondition <- factor(modeling_data$PhysicalCondition,
                                          levels=c("UN","VP","PR","FR","AV",
                                                   "GD","VG","EX"),labels=c(1:8))

modeling_data$Quality <- factor(modeling_data$Quality, levels=c("E-","E","E+",
                                                                "D-","D","D+",
                                                                "C-","C","C+",
                                                                "B-","B","B+",
                                                                "A-","A","A+",
                                                                "AA-","AA","AA+"),
                                labels=c(1:18))

modeling_data$RatingBath <- factor(modeling_data$RatingBath,
                                          levels=c("UN","VP","PR","FR","AV",
                                                   "GD","VG","EX"),labels=c(1:8))

modeling_data$RatingHalfBath <- factor(modeling_data$RatingHalfBath,
                                   levels=c("UN","VP","PR","FR","AV",
                                            "GD","VG","EX"),labels=c(1:8))

modeling_data$RatingKitchen <- factor(modeling_data$RatingKitchen,
                                   levels=c("UN","VP","PR","FR","AV",
                                            "GD","VG","EX"),labels=c(1:8))
```

## Collapsing BuildingType

```{r}
#examine the effect of buildingtype on lastsaleprice to see which categories should be grouped together
summary(glm(LastSalePrice ~ BuildingType, family=Gamma(link="log"),data = modeling_data)) # i actually think we should remove this from the model based on this result. none are significant predictors here except mansion which is going to be highly correlated with the square footage of the house, a variable we already have that shows a lot of significance by itself
```

## Collapsing Quality

```{r}
#examine the effect of quality on lastsaleprice to see which categories should be grouped together
summary(glm(LastSalePrice ~ Quality,data=modeling_data, family=Gamma(link="log")))
#put all B grades, all A grades, and all AA grades together and label the other ones "worse quality" 

#collapse to new variable QualityC and drop original variable Quality
require(tidyverse)
collapsed_data <- modeling_data %>% 
  mutate(QualityC = case_when(
    Quality == 1 ~ "Worse",
    Quality == 2 ~ "Worse",
    Quality == 3 ~ "Worse",
    Quality == 4 ~ "Worse",
    Quality == 5 ~ "Worse",
    Quality == 6 ~ "Worse",
    Quality == 7 ~ "Worse",
    Quality == 8 ~ "Worse",
    Quality == 9 ~ "Worse",
    Quality == 10 ~ "B",
    Quality == 11 ~ "B",
    Quality == 12 ~ "B",
    Quality == 13 ~ "A",
    Quality == 14 ~ "A",
    Quality == 15 ~ "A",
    Quality == 16 ~ "AA",
    Quality == 17 ~ "AA",
    Quality == 18 ~ "AA"
  )) %>% 
  select(-c(Quality))
```

## Collapse PrimaryWall

```{r}
#examine to see how to collapse
summary(glm(LastSalePrice ~ PrimaryWall, data= collapsed_data,family=Gamma(link="log")))

#look at distribution
table(collapsed_data$PrimaryWall)
#aluminum/vinyl should be collapsed to one category and so should precast masonry and masonry/frame and prem wood and wood based on quantities 

#collapse categories to create primarywallc variable and remove original primarywall variable
collapsed_data <- collapsed_data %>% 
  mutate(PrimaryWallC = case_when(
    PrimaryWall == "Alum/Vynyl Siding" ~ "Aluminum/Vinyl",
    PrimaryWall == "Aluminum/Vinyl" ~ "Aluminum/Vinyl",
    PrimaryWall == "Masonry/Frame" ~ "Masonry",
    PrimaryWall == "PrecastMasonry" ~ "Masonry",
    PrimaryWall == "Asphalt/Other" ~ "Asphalt/Other",
    PrimaryWall == "Block" ~ "Block",
    PrimaryWall == "Brick" ~ "Brick",
    PrimaryWall == "Fiber Cement/Hardiplank" ~ "Fiber Cement/Hardiplank",
    PrimaryWall == "Prem Wood" ~ "Wood",
    PrimaryWall == "Wood" ~ "Wood",
    PrimaryWall == "Stone" ~ "Stone",
    PrimaryWall == "Stucco" ~ "Stucco"
   
  )) %>% 
  select(-c(PrimaryWall))
```

## We should remove GEO_TRACT from our model as this is collinear with the other location variables and there are too many GEO_TRACTS to quickly collapse well. If we had time to cluster these that might be good, but I think neighborhood or neighborhood cluster would be a better measure.

now I'm getting an error that says "Warning: prediction from a rank-deficient fit may be misleading". check for collinearity

```{r}

#use this model to test for collinearity by adding and removing variables one by one

test_model <- glm(LastSalePrice ~ RatingBath  + AsphaltPaving +  FiberglassPool +GreenHouse +ReinforcedConcreteSF + MetalShed + Canopy  + MiscSfyi  + FrameShed + Parking + PhysicalCondition + YearBuilt + QualityC + FullBath + HalfBath +   Kitchen +  PrimaryWallC +  TotalFinishedArea + LandSF +  AirConditioned  + XCoordinate + YCoordinate + factor(NeighborhoodCluster) + MasonAdjustment+ Valuation2021 + Valuation2020 + Valuation2019 + PlasticLinedPool  + PrefabPool + DivingBoard  + PoolLadder + PoolLighting , family=Gamma(link="log"),data=train_c)

# BlacktopParking, Patio, DetatchedGarage, GunitePool, RecRoom, ChainLinkFence, MasonryGarage, BasementParking, Attic, factor(Neighborhood), RatingKitchen +  RatingHalfBath, GEO_TRACT a problem in terms of collinearity when adding back into the model

mean((predict(test_model,newdata = test_c) - test_c$LastSalePrice)**2) #now this is giving NA.


table(collapsed_data$Patio) #only 4 properties have patios -- remove this variable

table(collapsed_data$GunitePool) #only one property has 1 -- remove this variable

table(collapsed_data$RecRoom) #no properties have any. remove this variable

table(collapsed_data$ChainLinkFence) #one property has 2. that is all. remove this variable

table(collapsed_data$Attic) #no properties have any. remove this variable

#rating kitchen is pretty collinear with rating bath. keep rating_kitchen out 
cramerV(collapsed_data$RatingKitchen, collapsed_data$RatingBath)

#make a variable that's just "parking" and remove those other variables with few or no observations 
collapsed_data <- collapsed_data %>% 
  mutate(Parking = BlacktopParking + DetatchedGarage + MasonryGarage + BasementParking + Carport + FrameGarage+BrickGarage  +ConcreteParking + SurfaceParking) %>% 
  select(-c(BlacktopParking,DetatchedGarage,MasonryGarage,BasementParking,Carport,FrameGarage,BrickGarage, ConcreteParking, SurfaceParking,Patio, GunitePool,RecRoom,ChainLinkFence,Attic,RatingKitchen,RatingHalfBath))

summary(collapsed_data)

#the biggest problem with NA's is in HalfBath. I am going to change those NA's to 0, and then drop the rest of the NA's in this data set because there are NOT that many. most have 13 NA's so they might even be missing from the same ParcelID

collapsed_data$HalfBath[is.na(collapsed_data$HalfBath)] <- 0
collapsed_data$FullBath[is.na(collapsed_data$FullBath)] <- 0

#remove geotract from the data set because it has 507 NA's and dropping them would remove too many houses from the data set

#now drop NA and it shouldn't remove that many
collapsed_data_dropped_NA <- collapsed_data %>% 
  select(-c(GEO_TRACT)) %>% 
  drop_na() #this removed about 130 observations. 19789 --> 19656. I think this is acceptable. We still have a ton of observations. now try the MSE calc again

```

This test and train works and gives a real value for MSE. Amazing!!! Send to Charles.

```{r}
write.csv(collapsed_data_dropped_NA,"Fixed Data for Modeling.csv")
write.csv(train_c,"Training Data.csv")
write.csv(test_c, "Testing Data.csv")
```
