---
title: "GLM Modeling"
author: "Rachel Jordan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare data for modeling

```{r}
#load data set
modeling_data_raw <- read.csv("All Data for Modeling.csv",header=T)
modeling_data <- modeling_data_raw

#drop property ID, parcel ID, lastsaledate
modeling_data <- modeling_data %>% 
  select(-c(PropertyID,ParcelID,LastSaleDate))

#relevel factors
modeling_data$PhysicalCondition <- factor(modeling_data$PhysicalCondition,
                                          levels=c("UN","VP","PR","FR","AV",
                                                   "GD","VG","EX"),labels=c(1:8))

modeling_data$Quality <- factor(modeling_data$Quality, levels=c("E-","E","E+",
                                                                "D-","D","D+",
                                                                "C-","C","C+",
                                                                "B-","B","B+",
                                                                "A-","A","A+",
                                                                "AA-","AA","AA+"),
                                labels=c(1:18))

modeling_data$RatingBath <- factor(modeling_data$RatingBath,
                                          levels=c("UN","VP","PR","FR","AV",
                                                   "GD","VG","EX"),labels=c(1:8))

modeling_data$RatingHalfBath <- factor(modeling_data$RatingHalfBath,
                                   levels=c("UN","VP","PR","FR","AV",
                                            "GD","VG","EX"),labels=c(1:8))

modeling_data$RatingKitchen <- factor(modeling_data$RatingKitchen,
                                   levels=c("UN","VP","PR","FR","AV",
                                            "GD","VG","EX"),labels=c(1:8))
```

## Split into train and test sets

```{r}
#split into train and test sets
library(caTools)
#make this example reproducible
set.seed(2022)
#use 80% of dataset as training set and 20% as test set
sample <- sample.split(modeling_data$HalfBath, SplitRatio = 0.8)
train  <- subset(modeling_data, sample == TRUE)
test   <- subset(modeling_data, sample == FALSE)
```

## Implementing the bestglm() function

```{r}
#load bestglm package
require(bestglm)

###arranging the data correctly
#load tidyverse
require(tidyverse)
#move LastSalePrice to front and change name to y and removing duplicate last sale price variable
modeling_data_for_best_glm <- modeling_data %>% 
  mutate(y = LastSalePrice) %>% 
  select(y, everything()) %>% 
  select(-c(LastSalePrice))

#bestglm_model <- bestglm(modeling_data_for_best_glm,family=Gamma(link="log"))
```

## Performing purposeful variable selection

Steps from Agresti book section 5.1.4

1.  Construct an initial main-effects model using explanatory variables that include the known important variables and others that show any evidence of being relevant when used as sole predictors (e.g. having p-value of \< 0.2)

```{r}
summary(glm(LastSalePrice ~ BuildingType,data=train,family=Gamma(link="log")))
#some are significant. KEEP

summary(glm(LastSalePrice ~ PhysicalCondition,data=train,family=Gamma(link="log"))) #bad conditions are more significant, but KEEP

summary(glm(LastSalePrice ~ as.factor(Neighborhood),data=train,family=Gamma(link="log")))
#definitely significant. KEEP

summary(glm(LastSalePrice ~ Quality,data=train,family=Gamma(link="log")))
#significant. KEEP

summary(glm(LastSalePrice ~ YearBuilt,data=train,family=Gamma(link="log")))
#significant. KEEP

summary(glm(LastSalePrice ~ FullBath,data=train,family=Gamma(link="log")))
#definitely significant. KEEP

summary(glm(LastSalePrice ~ RatingBath,data=train,family=Gamma(link="log")))
#significant at the low ends and the high ends, KEEP

summary(glm(LastSalePrice ~ HalfBath,data=train,family=Gamma(link="log")))
#almost significant - KEEP

summary(glm(LastSalePrice ~ RatingHalfBath,data=train,family=Gamma(link="log")))
#significant at the low ends and the high ends, KEEP

summary(glm(LastSalePrice ~ Kitchen,data=train,family=Gamma(link="log")))
#close to significant, KEEP

summary(glm(LastSalePrice ~ RatingKitchen,data=train,family=Gamma(link="log")))
#significant at the low end, KEEP

summary(glm(LastSalePrice ~ PrimaryWall,data=train,family=Gamma(link="log")))
#asphalt and aluminum are almost significant, maybe make those dummy variables? Keep for now

summary(glm(LastSalePrice ~ TotalFinishedArea,data=train,family=Gamma(link="log")))
#obviously super significant, KEEP

summary(glm(LastSalePrice ~ LandSF,data=train,family=Gamma(link="log")))
#significant, KEEP

summary(glm(LastSalePrice ~ SeasonSold,data=train,family=Gamma(link="log")))
#almost significant, wait but we're not going to have that data for the houses we're trying to predict on, so DROP THIS VARIABLE ACTUALLY BECAUSE IT WILL NOT HELP OUR MAIN GOAL

summary(glm(LastSalePrice ~ AirConditioned,data=train,family=Gamma(link="log")))
#significant, KEEP

summary(glm(LastSalePrice ~ FrameShed,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ FrameGarage,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ MasonAdjustment,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ MiscSfyi,data=train,family=Gamma(link="log")))
#keep omg why is the coefficient negative?? are misc special features bad

summary(glm(LastSalePrice ~ PlasticLinedPool,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ PrefabPool,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ Canopy,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ MetalShed,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ SurfaceParking,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ ConcreteParking,data=train,family=Gamma(link="log")))
#drop, but I wonder if we made a variable that was just a general parking yes/no dummy if that would be significant

summary(glm(LastSalePrice ~ BrickGarage,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ DivingBoard,data=train,family=Gamma(link="log")))
#this is significant but probably just because pool is significant, keep for now

summary(glm(LastSalePrice ~ PoolLadder,data=train,family=Gamma(link="log")))
#see note above

summary(glm(LastSalePrice ~ ReinforcedConcreteSF,data=train,family=Gamma(link="log")))
#super significant. maybe ask colin what this is. keep

summary(glm(LastSalePrice ~ BlacktopParking,data=train,family=Gamma(link="log")))
#drop, there are no instances of this in the data

summary(glm(LastSalePrice ~ GreenHouse,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ FiberglassPool,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ Patio,data=train,family=Gamma(link="log")))
#drop, there are no instances of this in the data

summary(glm(LastSalePrice ~ PoolLighting,data=train,family=Gamma(link="log")))
#significant but probably just bc theres a pool

summary(glm(LastSalePrice ~ DetatchedGarage,data=train,family=Gamma(link="log")))
#drop, no instances of this in the data

summary(glm(LastSalePrice ~ FrameGarage,data=train,family=Gamma(link="log")))
#keep

summary(glm(LastSalePrice ~ AsphaltPaving,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ Carport,data=train,family=Gamma(link="log")))
#drop

summary(glm(LastSalePrice ~ GunitePool,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ RecRoom,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ ChainLinkFence,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ MasonryGarage,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ BasementParking,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ Attic,data=train,family=Gamma(link="log")))
#drop, none in data

summary(glm(LastSalePrice ~ Valuation2020,data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ Valuation2021,data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ Valuation2019,data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ XCoordinate,data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ YCoordinate,data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ as.factor(NeighborhoodCluster),data=train,family=Gamma(link="log")))
#super significant, keep

summary(glm(LastSalePrice ~ as.factor(GEO_TRACT),data=train,family=Gamma(link="log")))
#super significant, keep. maybe we can play with which of the location variables gives us the best result because we don't need all of them
```

Step 2. Conduct backward elimination, keeping a variable if it is either significant at a somewhat more stringent level or shows evidence of being a relevant confounder, in the sense that the estimated effect of a key variable changes substantially when it is removed.

```{r}
options(max.print = 10000000)
model_1_bw <- glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + MasonAdjustment + MiscSfyi + PlasticLinedPool + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + ReinforcedConcreteSF + FiberglassPool + PoolLighting + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log")) #remove reinforcedconcreteSF, p value of 0.988

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + MasonAdjustment + MiscSfyi + PlasticLinedPool + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FiberglassPool + PoolLighting + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove MiscSfyi 0.959

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + MasonAdjustment + PlasticLinedPool + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FiberglassPool + PoolLighting + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove plasticlinedpool

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + MasonAdjustment + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FiberglassPool + PoolLighting + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove poollighting

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + MasonAdjustment + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FiberglassPool + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove masonadjustment

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FiberglassPool + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove fiberglass pool

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + PrefabPool + MetalShed + BrickGarage + DivingBoard + PoolLadder + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove diving board 

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + AirConditioned + FrameGarage + PrefabPool + MetalShed + BrickGarage + PoolLadder + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove air conditioning 

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + PrimaryWall + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + PoolLadder + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove primary wall

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen + RatingKitchen + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + PoolLadder + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove rating kitchen

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen  + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + PoolLadder + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove pool ladder

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + RatingBath + HalfBath + RatingHalfBath + Kitchen  + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove ratingbath

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + HalfBath + RatingHalfBath + Kitchen  + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + FrameGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove framegarage

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + HalfBath + RatingHalfBath + Kitchen  + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove rating half bath

summary(glm(LastSalePrice ~ BuildingType + PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + HalfBath  + Kitchen  + TotalFinishedArea + LandSF + FrameGarage + PrefabPool + MetalShed + BrickGarage + Valuation2020 + Valuation2021 + Valuation2019 + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove frame garage

middle_model_bw <- summary(glm(LastSalePrice ~  PhysicalCondition + factor(Neighborhood) + Quality + YearBuilt + FullBath + HalfBath  + Kitchen  + TotalFinishedArea + LandSF  + PrefabPool + MetalShed + BrickGarage + Valuation2020 + Valuation2021 + Valuation2019 +  RatingHalfBath + XCoordinate + YCoordinate,data=train,family=Gamma(link="log"))) #remove frame garage

#check in on this little buddy and see if it's improved since first model from this section

require(boot)
mean((predict(model_1_bw,newdata = test) - test$LastSalePrice)**2)
```
