---
title: "Purposeful Variable Selection with Gamma GLM"
author: "Rachel Jordan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load data

```{r}
testing <- read.csv("Testing Data.csv",header=T)
training <- read.csv("Training Data.csv",header=T)

```

Step 1: Construct an initial main-effects model using explanatory variables that include the known important variables and others that show any evidence of being relevant when used as sole predictors (e.g., having P-value \< 0.2).

```{r}
summary(glm(LastSalePrice ~ BuildingType,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ factor(PhysicalCondition),data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ factor(Neighborhood),data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ YearBuilt,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ FullBath,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ factor(RatingBath),data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ HalfBath,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ Kitchen,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ TotalFinishedArea,data=training,family=Gamma(link="log"))) #keep

summary(glm(LastSalePrice ~ LandSF,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ AirConditioned,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ FrameShed,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ MasonAdjustment,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ MiscSfyi,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ PlasticLinedPool,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ PrefabPool,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ Canopy,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ MetalShed,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ DivingBoard,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ PoolLadder,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ ReinforcedConcreteSF,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ GreenHouse,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ FiberglassPool,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ PoolLighting,data=training,family=Gamma(link="log"))) 
############DROP

summary(glm(LastSalePrice ~ FrameGarage.1,data=training,family=Gamma(link="log"))) 
###########DROP

summary(glm(LastSalePrice ~ AsphaltPaving,data=training,family=Gamma(link="log"))) 
##########DROP

summary(glm(LastSalePrice ~ Valuation2021,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ XCoordinate,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ YCoordinate,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ factor(NeighborhoodCluster),data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ QualityC,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ PrimaryWallC,data=training,family=Gamma(link="log"))) 
#keep

summary(glm(LastSalePrice ~ Parking,data=training,family=Gamma(link="log"))) 
#keep

```

Test model that results from just keeping the variables that are significant in step 1

```{r}
step1_model <- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + Valuation2021 + XCoordinate + YCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

mean((predict(step1_model,newdata=testing,type="response") - testing$LastSalePrice)**2) #2,420,246,419

mean(((predict(step1_model,newdata=testing,type="response") - testing$LastSalePrice)/testing$LastSalePrice)) #just over 11% off for each house

#assessment sales ratio
require(stats)
median((predict(step1_model,newdata=testing,type="response")/testing$LastSalePrice)) #1.05

#remove neighborhood or neighborhoood cluster because they make it rank-deficient and "misleading". using neighborhoodcluster results in a slightly worse model in terms of both sales ratio and COD so use neighborhood

#coefficient of dispersion
sales_ratios_glm <- predict(step1_model,newdata=testing,type="response")/testing$LastSalePrice
median_glm <- median(sales_ratios_glm)
mean((sales_ratios_glm-median_glm)/median_glm) #0.062 < 0.15


```

Trying a linear model

```{r}
linear_model <- lm(LastSalePrice ~ factor(PhysicalCondition) + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + Valuation2021 + XCoordinate + YCoordinate + QualityC + PrimaryWallC + Parking,data=training)

mean((predict(linear_model,newdata = testing) - testing$LastSalePrice)**2) #2,017,051,097

mean(((predict(linear_model,newdata=testing) - testing$LastSalePrice)/testing$LastSalePrice)) #we are just over 10% off on average for each house

#assessment sales ratio
median((predict(linear_model,newdata=testing)/testing$LastSalePrice)) #1.05

#coefficient of dispersion
sales_ratios_lm <- predict(linear_model,newdata=testing)/testing$LastSalePrice
median_lm <- median(sales_ratios_lm)
mean((sales_ratios_lm-median_lm)/median_lm) #0.05 > 0.15

#remove valuation2021
linear_model_2 <- lm(LastSalePrice ~ factor(PhysicalCondition) + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + XCoordinate + YCoordinate + QualityC + PrimaryWallC + Parking,data=training)

#assessment sales ratio
median((predict(linear_model_2,newdata=testing)/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_lm_2 <- predict(linear_model_2,newdata=testing)/testing$LastSalePrice
median_lm_2 <- median(sales_ratios_lm_2)
mean((sales_ratios_lm_2-median_lm_2)/median_lm_2) #0.053 < 0.15

```

Step 2: Conduct backward elimination, keeping a variable if it is either significant at a somewhat more stringent level or shows evidence of being a relevant confounder, in the sense that the estimated effect of a key variable changes substantially when it is removed.

```{r}
#continue with step 2 of purposeful variable selection

step2_model_1<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + XCoordinate + YCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))
#remove valuation2021 because Colin said that valuations are red herrings

#assessment sales ratio
median((predict(step2_model_1,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_2 <- predict(step2_model_1,newdata=testing,type="response")/testing$LastSalePrice
median_glm_2 <- median(sales_ratios_glm_2)
mean((sales_ratios_glm_2-median_glm_2)/median_glm_2) #0.067 < 0.15

#decide which variable to remove
summary(step2_model_1) #drop YCoordinate - p-value 0.948

step2_model_2<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_2,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_3 <- predict(step2_model_2,newdata=testing,type="response")/testing$LastSalePrice
median_glm_3 <- median(sales_ratios_glm_3)
mean((sales_ratios_glm_3-median_glm_3)/median_glm_3) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_2) #drop reinforcedconcreteSF - p-value 0.947

step2_model_3<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_3,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_4 <- predict(step2_model_3,newdata=testing,type="response")/testing$LastSalePrice
median_glm_4 <- median(sales_ratios_glm_4)
mean((sales_ratios_glm_4-median_glm_4)/median_glm_4) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_3) #drop plasticlinepool - p-value 0.899

step2_model_4<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + DivingBoard + PoolLadder + ReinforcedConcreteSF + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_4,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_5 <- predict(step2_model_2,newdata=testing,type="response")/testing$LastSalePrice
median_glm_5 <- median(sales_ratios_glm_5)
mean((sales_ratios_glm_5-median_glm_5)/median_glm_5) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_4) #drop reinforcedconcreteSF - p-value 0.95

step2_model_5<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + DivingBoard + PoolLadder + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_5,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_6 <- predict(step2_model_5,newdata=testing,type="response")/testing$LastSalePrice
median_glm_6 <- median(sales_ratios_glm_6)
mean((sales_ratios_glm_6-median_glm_6)/median_glm_6) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_5) #drop frameshed - p-value 0.89

step2_model_6<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + MasonAdjustment + DivingBoard + PoolLadder + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_6,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_7 <- predict(step2_model_6,newdata=testing,type="response")/testing$LastSalePrice
median_glm_7 <- median(sales_ratios_glm_7)
mean((sales_ratios_glm_7-median_glm_7)/median_glm_7) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_6) #drop divingboard - p-value 0.822

step2_model_7<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + MasonAdjustment + PoolLadder + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_7,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_8 <- predict(step2_model_7,newdata=testing,type="response")/testing$LastSalePrice
median_glm_8 <- median(sales_ratios_glm_8)
mean((sales_ratios_glm_8-median_glm_8)/median_glm_8) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_7) #drop poolladder - p-value 0.83

step2_model_8<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + MasonAdjustment + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_8,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_9 <- predict(step2_model_8,newdata=testing,type="response")/testing$LastSalePrice
median_glm_9 <- median(sales_ratios_glm_9)
mean((sales_ratios_glm_9-median_glm_9)/median_glm_9) #0.067 < 0.15

#metrics did not change much

#decide which variable to remove
summary(step2_model_8) #drop masonadjustment - p-value 0.20

step2_model_9<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_10 <- predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice
median_glm_10 <- median(sales_ratios_glm_10)
mean((sales_ratios_glm_10-median_glm_10)/median_glm_10) #0.066 < 0.15

#metrics did not change much - improved VERY slightly?

#decide which variable to remove
summary(step2_model_9) #drop qualityc - best p-value 0.079

step2_model_10<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_10,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_11 <- predict(step2_model_10,newdata=testing,type="response")/testing$LastSalePrice
median_glm_11 <- median(sales_ratios_glm_11)
mean((sales_ratios_glm_11-median_glm_11)/median_glm_11) #0.067 < 0.15

#metrics did not change much - got SLIGHTLY worse than previous model

#decide which variable to remove
summary(step2_model_10) #everything in the model is significant now. I'm going to revert to the model with qualityc because the metrics were SLIGHTLY better. 
```

Step 3: Add to the model any variables that were not included in step 1 but that are significant when adjusting for the variables in the model after step 2, since a variable may not be significantly associated with y but may make an important contribution in the presence of other variables.

```{r}
#the best model from previous step
step2_model_9<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_10 <- predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice
median_glm_10 <- median(sales_ratios_glm_10)
mean((sales_ratios_glm_10-median_glm_10)/median_glm_10) #0.066 < 0.15

#variables removed were MiscSFyi PrefabPool Canopy MetalShed GreenHouse FiberglassPool PoolLighting FrameGarage.1 AsphaltPaving

#add back MiscSfyi
step3_model_1<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + MiscSfyi,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_1,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_12 <- predict(step3_model_1,newdata=testing,type="response")/testing$LastSalePrice
median_glm_12 <- median(sales_ratios_glm_12)
mean((sales_ratios_glm_12-median_glm_12)/median_glm_12) #0.067 < 0.15

summary(step3_model_1) #not significant and does not improve metrics

#add back PrefabPool
step3_model_2<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + PrefabPool,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_2,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_13 <- predict(step3_model_2,newdata=testing,type="response")/testing$LastSalePrice
median_glm_13 <- median(sales_ratios_glm_13)
mean((sales_ratios_glm_13-median_glm_13)/median_glm_13) #0.067 < 0.15

summary(step3_model_2) #not significant and does not improve metrics

#add back Canopy
step3_model_3<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + Canopy,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_3,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_14 <- predict(step3_model_3,newdata=testing,type="response")/testing$LastSalePrice
median_glm_14 <- median(sales_ratios_glm_14)
mean((sales_ratios_glm_14-median_glm_14)/median_glm_14) #0.067 < 0.15

summary(step3_model_3) #not significant and does not improve metrics

#add back MetalShed
step3_model_4<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + MetalShed,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_4,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_15 <- predict(step3_model_4,newdata=testing,type="response")/testing$LastSalePrice
median_glm_15 <- median(sales_ratios_glm_15)
mean((sales_ratios_glm_15-median_glm_15)/median_glm_15) #0.067 < 0.15

summary(step3_model_4) #not significant and does not improve metrics

#add back GreenHouse
step3_model_5<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + GreenHouse,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_5,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_16 <- predict(step3_model_5,newdata=testing,type="response")/testing$LastSalePrice
median_glm_16 <- median(sales_ratios_glm_16)
mean((sales_ratios_glm_16-median_glm_16)/median_glm_16) #0.066 < 0.15

summary(step3_model_5) #not significant and does not improve metrics

#add back FiberglassPool
step3_model_6<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FiberglassPool,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_6,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_17 <- predict(step3_model_6,newdata=testing,type="response")/testing$LastSalePrice
median_glm_17 <- median(sales_ratios_glm_17)
mean((sales_ratios_glm_17-median_glm_17)/median_glm_17) #0.067 < 0.15

summary(step3_model_6) #not significant and does not improve metrics

#add back PoolLighting
step3_model_7<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + PoolLighting,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_7,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_18 <- predict(step3_model_7,newdata=testing,type="response")/testing$LastSalePrice
median_glm_18 <- median(sales_ratios_glm_18)
mean((sales_ratios_glm_18-median_glm_18)/median_glm_18) #0.066 < 0.15

summary(step3_model_7) #not significant and does not improve metrics

#add back FrameGarage.1
step3_model_8<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FrameGarage.1,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_8,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_19 <- predict(step3_model_8,newdata=testing,type="response")/testing$LastSalePrice
median_glm_19 <- median(sales_ratios_glm_19)
mean((sales_ratios_glm_19-median_glm_19)/median_glm_19) #0.067 < 0.15

summary(step3_model_8) #not significant and does not improve metrics

#add back AsphaltPaving
step3_model_9<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + AsphaltPaving,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step3_model_9,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_20 <- predict(step3_model_9,newdata=testing,type="response")/testing$LastSalePrice
median_glm_20 <- median(sales_ratios_glm_20)
mean((sales_ratios_glm_20-median_glm_20)/median_glm_20) #0.066 < 0.15

summary(step3_model_9) #not significant and does not improve metrics
```

Step 4: Check for plausible interactions among variables in the model after step 3, using significance tests at conventional levels such as 0.05.

```{r}
#the best model from previous step
step2_model_9<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking,data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_10 <- predict(step2_model_9,newdata=testing,type="response")/testing$LastSalePrice
median_glm_10 <- median(sales_ratios_glm_10)
mean((sales_ratios_glm_10-median_glm_10)/median_glm_10) #0.066 < 0.15

#check PhysicalCondition*Neighborhood
step4_model_1<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + factor(PhysicalCondition)*factor(Neighborhood), data=training,family=Gamma(link="log"))
#this gave a warning about rank-deficient-fit 

#assessment sales ratio
median((predict(step4_model_1,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_21 <- predict(step4_model_1,newdata=testing,type="response")/testing$LastSalePrice
median_glm_21 <- median(sales_ratios_glm_21)
mean((sales_ratios_glm_21-median_glm_21)/median_glm_21) #Inf

#check FullBath*TotalFinishedArea
step4_model_2<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step4_model_2,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_22 <- predict(step4_model_2,newdata=testing,type="response")/testing$LastSalePrice
median_glm_22 <- median(sales_ratios_glm_22)
mean((sales_ratios_glm_22-median_glm_22)/median_glm_22) #0.064 < 0.15

summary(step4_model_2) #the interaction is significant and slightly improves the model

#add HalfBath*TotalFinishedArea
step4_model_3<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step4_model_3,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_23 <- predict(step4_model_3,newdata=testing,type="response")/testing$LastSalePrice
median_glm_23 <- median(sales_ratios_glm_23)
mean((sales_ratios_glm_23-median_glm_23)/median_glm_23) #0.064 < 0.15

summary(step4_model_3) #the interaction is significant and slightly improves the model

#add LandSF*TotalFinishedArea
step4_model_4<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea + LandSF*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step4_model_4,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_24 <- predict(step4_model_4,newdata=testing,type="response")/testing$LastSalePrice
median_glm_24 <- median(sales_ratios_glm_24)
mean((sales_ratios_glm_24-median_glm_24)/median_glm_24) #0.064 < 0.15

summary(step4_model_4) #the interaction is not significant and doesn't really improve the model

#add AirConditioned*factor(Neighborhood)
step4_model_5<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea + AirConditioned*factor(Neighborhood), data=training,family=Gamma(link="log"))
#rank-deficient fit warning

#assessment sales ratio
median((predict(step4_model_5,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_25 <- predict(step4_model_5,newdata=testing,type="response")/testing$LastSalePrice
median_glm_25 <- median(sales_ratios_glm_25)
mean((sales_ratios_glm_25-median_glm_25)/median_glm_25) #0.064 < 0.15

summary(step4_model_5) #the interaction is not significant and doesn't really improve the model

#add YearBuilt*TotalFinishedArea
step4_model_6<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea + YearBuilt*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step4_model_6,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_26 <- predict(step4_model_6,newdata=testing,type="response")/testing$LastSalePrice
median_glm_26 <- median(sales_ratios_glm_26)
mean((sales_ratios_glm_26-median_glm_26)/median_glm_26) #0.065 < 0.15

summary(step4_model_6) #the interaction is not significant and doesn't really improve the model
```

Best model so far

```{r}
#best model
step4_model_3<- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(step4_model_3,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_23 <- predict(step4_model_3,newdata=testing,type="response")/testing$LastSalePrice
median_glm_23 <- median(sales_ratios_glm_23)
mean((sales_ratios_glm_23-median_glm_23)/median_glm_23) #0.064 < 0.15

#try square root transformation on YearBuilt suggested by client
best_model_tr <- glm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + sqrt(YearBuilt) + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea, data=training,family=Gamma(link="log"))

#assessment sales ratio
median((predict(best_model_tr,newdata=testing,type="response")/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_glm_27 <- predict(best_model_tr,newdata=testing,type="response")/testing$LastSalePrice
median_glm_27 <- median(sales_ratios_glm_27)
mean((sales_ratios_glm_27-median_glm_27)/median_glm_27) #0.064 < 0.15
#didn't really do much

#wait for client to suggest other plausible interaction terms
```

Is that model better than bestGLM?

```{r}
#rerun bestglm because I think this is an old one
#assessment sales ratio for bestglm
median((predict(bestglm_model$BestModel,newdata=best_glm_testing,type="response")/testing$LastSalePrice)) #1.05

#coefficient of dispersion for bestglm
sales_ratios_bestglm <- predict(bestglm_model$BestModel,newdata=best_glm_testing,type="response")/testing$LastSalePrice
median_bestglm <- median(sales_ratios_bestglm)
mean((sales_ratios_bestglm-median_bestglm)/median_bestglm) #0.088 < 0.15

summary(bestglm_model$BestModel)

#try the bestglm model with neighborhood instead of neighborhood cluster
best_glm_neighb <- glm(LastSalePrice ~ factor(PhysicalCondition) + YearBuilt + HalfBath + TotalFinishedArea + LandSF + AirConditioned + factor(Neighborhood) + factor(QualityC) + PrimaryWallC + Parking, data= training, family=Gamma(link="log"))

#assessment sales ratio
median((predict(best_glm_neighb,newdata=testing,type="response")/testing$LastSalePrice)) #1.05

#coefficient of dispersion for bestglm
sales_ratios_bestglm_2<- predict(best_glm_neighb,newdata=best_glm_testing,type="response")/testing$LastSalePrice
median_bestglm_2 <- median(sales_ratios_bestglm_2)
mean((sales_ratios_bestglm_2-median_bestglm_2)/median_bestglm_2) #0.068 < 0.15

#still not better than what we found with purposeful variable selection
```

Compare and tinker with best linear model

```{r}
#try your best GLM result as a linear model
linear_model_3 <- lm(LastSalePrice ~ factor(PhysicalCondition)  + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + XCoordinate + QualityC + PrimaryWallC + Parking + FullBath*TotalFinishedArea + HalfBath*TotalFinishedArea, data=training)

#assessment sales ratio
median((predict(linear_model_3,newdata=testing)/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_lm_3 <- predict(linear_model_3,newdata=testing)/testing$LastSalePrice
median_lm_3 <- median(sales_ratios_lm_3)
mean((sales_ratios_lm_3-median_lm_3)/median_lm_3) #0.054 < 0.15
```

Initial linear model is the best.

```{r}
#best model
linear_model_2 <- lm(LastSalePrice ~ factor(PhysicalCondition) + factor(Neighborhood) + YearBuilt + FullBath + factor(RatingBath) + HalfBath + Kitchen + TotalFinishedArea + LandSF + AirConditioned + FrameShed + MasonAdjustment + PlasticLinedPool + DivingBoard + PoolLadder + ReinforcedConcreteSF + XCoordinate + YCoordinate + QualityC + PrimaryWallC + Parking,data=training)

#assessment sales ratio
median((predict(linear_model_2,newdata=testing)/testing$LastSalePrice)) #1.04

#coefficient of dispersion
sales_ratios_lm_2 <- predict(linear_model_2,newdata=testing)/testing$LastSalePrice
median_lm_2 <- median(sales_ratios_lm_2)
mean((sales_ratios_lm_2-median_lm_2)/median_lm_2) #0.053 < 0.15

summary(linear_model_2)
```
